Genome-wide changes in expression during inflorescence architecture development

### 2015-09-16 ms.Rmd
adjusted figures for new version of oryza::LocToGeneNames()

---
title: Genome-wide changes in expression during inflorescence architecture development
  in rice
csl: csl/the-plant-journal.csl
header-includes: \usepackage{graphicx}
output:
  BiocStyle::html_document:
    fig_caption: yes
    force_captions: yes
    highlight: pygments
    number_sections: yes
    dev: "CairoPDF"
  word_document:
    fig_caption: yes
    reference_docx: csl/wordStyles.docx
  pdf_document:
    fig_caption: yes
    number_sections: yes
bibliography: bib/papersLib.bibtex
---

@@

## MADS genes: comparison of expression & homology in rice, tomato, arabidopsis

>>>>

---
title: Genome-wide changes in expression during inflorescence architecture development
  in rice
csl: csl/the-plant-journal.csl
header-includes: \usepackage{graphicx}
output:
  BiocStyle::html_document:
    fig_caption: yes
    force_captions: yes
    highlight: pygments
    number_sections: yes
    dev: "CairoPDF"
    toc: true
  word_document:
    fig_caption: yes
    reference_docx: csl/wordStyles.docx
  pdf_document:
    fig_caption: yes
    number_sections: yes
bibliography: bib/papersLib.bibtex
---

@@

## Evolution of MADS genes in monocots and dicots
